---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTPkMrSw1lZWYlizNVWxtyjwJTJq47H6w0EU5NlcyrUqySC4ZvtPZzUhVUZ-Gwkb6zNtE-bNvC9mfzK/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    category = `What category was the video?`,
    length_seconds = `What was the length of the video (seconds)`,
    finished_seconds = `How Much of the Short did u finish (in seconds)`,
    engagement = `Rate the video engagement out of 10`,
    likes = `How many likes does the short have?`
  )

summary_values <- latest_data %>%
  summarise(
    mean_length = mean(length_seconds),
    mean_engagement = mean(engagement)
  )

```

```{css}
body {
  font-family: Arial, sans-serif;
  background-color: #f8f8f8;
  color: #222222;
}

h2 {
  color: #6a0dad;
}

p {
  font-size: 16px;
  line-height: 1.5;
}
```

## What's going on with this data?

## YouTube Shorts Viewing Habits

This dynamic report shows patterns in the YouTube Shorts I logged using a Google Form. It focuses on the categories of shorts I watched and their engagement ratings.

The average length of the shorts in this dataset was **`r round(summary_values$mean_length, 2)` seconds**.

The average engagement rating of the shorts was **`r round(summary_values$mean_engagement, 2)` out of 10**.

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(y = category), fill = "#6a0dad") +
  labs(
    title = "Number of YouTube Shorts by Category",
    subtitle = "Count of the shorts I logged in each category",
    x = "Number of shorts",
    y = "Category",
    caption = "Source: Google Form data"
  )

latest_data %>%
  ggplot() +
  geom_bar(aes(x = engagement, fill = category)) +
  labs(
    title = "Engagement Scores of YouTube Shorts",
    subtitle = "Distribution of ratings out of 10",
    x = "Engagement score",
    y = "Number of shorts",
    caption = "Source: Google Form data"
  )
